\begin{thebibliography}{site5}

\bibitem[1]{web01}
LE DEEP LEARNING PAS À PAS : LES CONCEPTS (1/2). 
\newblock
\url{https://www.technologies-ebusiness.com/enjeux-et-tendances/le-deep-learning-pas-a-pas}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[2]{web02}
Harry Pommier, 2020. [Fiche mémo] Réseau de neurones profond.
\newblock
\url{https://medium.zenika.com/fiche-m%C3%A9mo-r%C3%A9seau-de-neurones-profond-66f6bf48a472}.
\newblock [Consult{\'e}: 25/08/2020].

\bibitem[3]{web03}
Modèles basés sur le réflex : apprentissage automatique
\newblock
\url{https://stanford.edu/~shervine/l/fr/teaching/cs-221/pense-bete-modeles-reflex}.
\newblock [Consult{\'e}: 08/08/2020].

\bibitem[4]{web04}
La rétropropagation du gradient. 
\newblock
\url{https://dataanalyticspost.com/Lexique/retropropagation/#:~:text=La%20r%C3%A9tropropagation%20du%20gradient%20de,dans%20une%20base%20d'apprentissage}.
\newblock [Consult{\'e}: 12/08/2020].

\bibitem[5]{web05}
Thierry Maubant. Qu'est-ce que le surapprentissage ?
\newblock
\url{https://www.actuia.com/faq/quest-ce-que-le-surapprentissage/}.
\newblock [Consult{\'e}: 07/08/2020].

\bibitem[6]{web06}
Artificial intelligence and the rise of economec inequality
\newblock
\url{https://www.datascience.us/artificial-intelligence-rise-economic-inequality/}.
\newblock [Consult{\'e}: 15/08/2020].

\bibitem[7]{web07}
Afshine Amidi et Shervine Amidi. (2018). Pense-bête de réseaux de neurones convolutionnels.
\newblock
\url{https://stanford.edu/~shervine/l/fr/teaching/cs-230/pense-bete-reseaux-neurones-convolutionnels}.

\bibitem[8]{web08}
Convolutional Neural Networks (CNN): Step 3 -Flattening.
\newblock
\url{https://www.superdatascience.com/blogs/convolutional-neural-networks-cnn-step-3-flattening}.
\newblock [Consult{\'e}: 22/08/2020].

\bibitem[9]{web09}
Par Jean-Pierre Mistral.(2018)   BIG DATA, INTELLIGENCE ARTIFICIELLE, APPRENTISSAGE AUTOMATIQUE ET LE RGPD.
\newblock
\url{https://www.village-justice.com/articles/big-data-intelligence-artificielle-apprentissage-automatique-rgpd,26838.html}.
\newblock [Consult{\'e}: 19/08/2020].

\bibitem[10]{web10}
Yarin Gal. What My Deep Model Doesn't Know
\newblock
\url{http://mlg.eng.cam.ac.uk/yarin/blog_3d801aa532c1ce.html}.
\newblock [Consult{\'e}: 28/08/2020].

\bibitem[11]{web11}
Robin Camarasa. Bayesian Deep Learning : Soyez sûr de vos incertitudes.
\newblock
\url{https://www.datagenius.fr/post/bayesian-deep-learning-soyez-sur-de-vos-incertitudes}.
\newblock [Consult{\'e}: 26/08/2020].

\bibitem[12]{web12}
Gábor Vecsei. Experiments with Monte-Carlo dropout for uncertainty estimation.
\newblock
\url{https://www.gaborvecsei.com/Monte-Carlo-Dropout/}.
\newblock [Consult{\'e}: 26/08/2020].

\bibitem[13]{web13}
Deep learning Dropout technical analysis.
\newblock
\url{https://www.programmersought.com/article/31754654312/}.
\newblock [Consult{\'e}: 28/08/2020].

\bibitem[14]{web14}
Python.
\newblock
\url{https://fr.wikibooks.org/wiki/Programmation_Python/Introduction}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[15]{web15}
Anaconda.
\newblock
\url{https://www.anaconda.com/what-is-anaconda/}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[16]{web16}
Pytorch.
\newblock
\url{https://datafranca.org/wiki/PyTorch}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[17]{web17}
Numpy.
\newblock
\url{https://openclassrooms.com/fr/courses/4452741-decouvrez-les-librairies-python-pour-la-data-science/4740941-plongez-en-detail-dans-la-librairie-numpy}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[18]{web18}
Matplotlib
\newblock
\url{https://matplotlib.org/}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[19]{web19}
HTML Tutorial.
\newblock
\url{https://www.w3schools.com/html/}.
\newblock [Consult{\'e}: 04/09/2020].

\bibitem[20]{web20}
CSS Tutorial.
\newblock
\url{https://www.w3schools.com/css/}.
\newblock [Consult{\'e}: 04/09/2020].

\bibitem[21]{web21}
JavaScript Tutorial
\newblock
\url{https://www.w3schools.com/js/}.
\newblock [Consult{\'e}: 04/09/2020].

\bibitem[22]{web22}
Create HTML User Interface for Python using Eel Library
\newblock
\url{https://medium.com/wronmbertech/create-html-user-interface-for-python-using-eel-library-bab101cc0f99}.
\newblock [Consult{\'e}: 04/09/2020].

\bibitem[23]{web23}
Pycharm
\newblock
\url{https://www.jetbrains.com/fr-fr/pycharm/}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[24]{web24}
Jupyter.
\newblock
\url{https://jupyter-notebook.readthedocs.io/en/stable/}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[25]{web25}
Cifar 10
\newblock
\url{http://www.cs.toronto.edu/~kriz/cifar.html}.
\newblock [Consult{\'e}: 06/08/2020].

\bibitem[26]{web26}
Useful Plots to Diagnose your Neural Network.
\newblock
\url{https://towardsdatascience.com/useful-plots-to-diagnose-your-neural-network-521907fa2f45}.
\newblock [Consult{\'e}: 28/08/2020].

\end{thebibliography}